 ---
title: "Hierarchical Model 1"
author: "Adriana F. Chávez De la Peña"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(R2jags)  #Load up packages
library(brms)
library(dplyr)

# Run from home (PV 2104)
load.module(name="wiener",
            path="/usr/lib/x86_64-linux-gnu/JAGS/lib/JAGS/modules-4/")

# Run from office
#load.module(name="wiener",
#            path="/usr/lib/JAGS/modules-4/")
```


# Load the data

```{r}
datos <- read.csv("../../../RawData/datos.csv")
datos <- datos[-which(datos$rt<50),]
datos <- datos[-which(datos$subID=="735148")]

N <- nrow(datos)
RT <- datos$rt
C <- datos$resp

J <- length(unique(datos$cond))
task <- rep(2,N)
task[datos$cond=="control"] <- 1

I <- length(unique(datos$subID))
subj <- as.factor(datos$subID)
levels(subj) <- c(1:I)

Y<-RT
Y[C==0] <- -RT[C==0]
```

# The model

\begin{align*}
Y = (Choice,RT)
\end{align*}

\begin{align*}
Y_{ijk} \sim \mbox{Wiener}(\alpha_j,\tau_j,\beta_j,\delta_j)
\end{align*}

with uninformative priors:

\begin{align*}
\alpha_j \sim \mbox{Uniform}(0,100)\\
\tau_j \sim \mbox{InverseGamma}(0.5,0.5)\\
\beta_j \sim \mbox{Uniform}(0,1)\\
\delta_j \sim \mbox{Normal}(0,20)\\
\end{align*}

where:

\begin{align*}
\alpha && \mbox{Threshold separation} && \alpha &> 0\\
\tau && \mbox{Non-decision time} && \tau &> 0\\
\beta && \mbox{Bias towards "Yes"} && 0 < &\beta < 1\\
\delta && \mbox{Drift rate} && \delta \sim &\mbox{Normal}(0,1)\\
\end{align*}

```{r}
write('
model {
  
  ###### Trial-by-trial variation
        for (i in 1:N) {
          Y[i] ~ dwiener(alpha[task[i]],tau[subj[i]],beta[task[i]],delta[i])
          delta[i] ~ dnorm(nu[subj[i],task[i]],pow(1,-2))
        }
  
  ###### Task-by-Participant mean drift rate
        for(i in 1:I){
          for(j in 1:J){
              nu[i,j] ~ dnorm(muNu,precNu)
          }
        }
        
  ###### Task-by-Participant mean drift rate
        for(i in 1:I){
            tau[i] ~ dnorm(muTau,precTau)
        }
  
  ###### Task-by-Participant mean drift rate
        for(j in 1:J){
            alpha[j] ~ dnorm(muAlpha,precAlpha)
            beta[j] ~ dnorm(muBeta,precBeta)
        }
  
  ################ PRIORS
        muBeta ~ dunif(0,1)
        sigmaBeta ~ dunif(0.0001,0.5)
        precBeta <- pow(sigmaBeta,-2) 
        
        muAlpha ~ dunif(0,500)
        sigmaAlpha ~ dunif(0.0001,1000)
        precAlpha <- pow(sigmaAlpha,-2) 
        
        muTau ~ dunif(0,1000)
        sigmaTau ~ dunif(0.0001,200)
        precTau <- pow(sigmaTau,-2) 
        
        muNu ~ dnorm(0,500)
        sigmaNu ~ dnorm(0.0001,1000)
        precNu <- pow(sigmaNu,-2) 
}',  'hierarchical_2.txt')
```

```{r}
y = Y*1000

dat <- list(Y = y,
            N = N,
            I = I,
            J = J,
            subj = subj,
            task = task)

inits <- list(alpha_high=rep(30,J),alpha_low=rep(10,J),
              tau_high=rep(200,J),tau_low=rep(10,J),
              mu.nu = rep(50,J), sigma.nu = rep(1,J), eta=10
              )
model <- jags.model("./hierarchical_W10.txt",data=dat,n.chains=1,n.adapt=0)#,inits=inits)
samples <- jags.samples(model,
                        c("alpha","beta","tau","delta","nu","sigmaDelta",
                          "muAlpha","muBeta","muTau","muNu",
                          "sigmaAlpha","sigmaBeta","sigmaTau","sigmaNu"), n.iter=10000,thin=1)

save(samples,file="./samples.RData")
```

```{r}
alpha <- samples$alpha[,,]
beta <- samples$beta[,,]
delta <- samples$delta[,,]
tau <- samples$tau[,,]
```

