---
title: "Modeling 101-A: A Wiener per Task"
author: "Adriana F. Chávez De la Peña"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(R2jags)  #Load up packages
library(brms)
library(dplyr)

# Run from home (PV 2104)
load.module(name="wiener",
            path="/usr/lib/x86_64-linux-gnu/JAGS/lib/JAGS/modules-4/")

# Run from office
#load.module(name="wiener",
#            path="/usr/lib/JAGS/modules-4/")
```

```{r, eval=FALSE}
#library(RWiener)

#Y <- rwiener(1000,alpha=100,delta=1,tau=1,beta = 0.5)
#hist(Y$q, breaks=20)
```

# Load the data

```{r}
datos <- read.csv("../../../00_RawMaterial/datos.csv")
datos <- datos[-which(datos$rt<50),]

I <- length(unique(datos$subID))
J <- length(unique(datos$cond))
N <- nrow(datos)

RT <- datos$rt
C <- datos$resp

task <- rep(2,N)
task[datos$cond=="control"] <- 1

subj <- as.factor(datos$subID)
levels(subj) <- c(1:I)

Y<-RT
Y[C==0] <- -RT[C==0]
```

# The model

\begin{align*}
Y = (Choice,RT)
\end{align*}

\begin{align*}
Y_{ijk} \sim \mbox{Wiener}(\alpha_j,\tau_j,\beta_j,\delta_j)
\end{align*}

with uninformative priors:

\begin{align*}
\alpha_j \sim \mbox{Uniform}(0,100)\\
\tau_j \sim \mbox{InverseGamma}(0.5,0.5)\\
\beta_j \sim \mbox{Uniform}(0,1)\\
\delta_j \sim \mbox{Normal}(0,20)\\
\end{align*}

where:

\begin{align*}
\alpha && \mbox{Threshold separation} && \alpha &> 0\\
\tau && \mbox{Non-decision time} && \tau &> 0\\
\beta && \mbox{Bias towards "Yes"} && 0 < &\beta < 1\\
\delta && \mbox{Drift rate} && \delta \sim &\mbox{Normal}(0,1)\\
\end{align*}

```{r}
write('
model {
  #Likelihood
  for (i in 1:N) {
    Y[i] ~ dwiener(alpha[i],tau[i],beta,delta[i])
    tau[i] ~ dunif(tau_low[task[i]],tau_high[task[i]])
    alpha[i] ~ dunif(alpha_low[task[i]],alpha_high[task[i]])
    delta[i] ~ dnorm(nu[task[i],subj[i]],eta)
  }
  
  #Priors
  for (j in 1:J) {
  tau_high[j] ~ dunif(0.01,500)
  tau_low[j] ~ dunif(0,tau_high[j])
  alpha_high[j] ~ dunif(0.01,500)
  alpha_low[j] ~ dunif(0,alpha_high[j])
  mu.nu[j] ~ dunif(-100,100)
  sigma.nu[j] ~ dunif(0.0001,100)
  prec.nu[j] <- pow(sigma.nu[j],-2)
  }
  
  for(i in 1:I){
    for(j in 1:J){
    nu[j,i] ~ dnorm(mu.nu[j],prec.nu[j])
    }
  }
  
  beta ~ dunif(0.4,0.6)
  eta ~ dgamma(2,2)
  
}',  'wienerW8a.txt')
```

```{r}
y = Y*1000

dat <- list(Y=y,N=N,I=I,J=J, subj=subj,task=task)
inits <- list(alpha_high=rep(30,J),alpha_low=rep(10,J),
              tau_high=rep(200,J),tau_low=rep(10,J),
              mu.nu = rep(50,J), sigma.nu = rep(1,J), eta=10
              )
model <- jags.model("./wienerW8a.txt",data=dat,n.chains=1,n.adapt=0)#,inits=inits)
samples <- jags.samples(model,c("nu","eta","alpha","beta","tau","delta","alpha_low",
                                "alpha_high","tau_low","tau_high","mu.nu","sigma.nu"),n.iter=10000,thin=1)
```

```{r}
par(mfrow=c(1,2))

beta <- samples$beta[1,,]

x <- seq(1,length(beta),length.out=5000)
plot(beta[x], pch=16, cex=0.5, type="l", ylab=expression(paste(beta)), xlab="Iteration")

plot(density(beta), xlim=c(min(beta),max(beta)), lwd=2, col="purple4",cex.main=1.2)
```


```{r}
par(mfrow=c(2,2))

alpha_low <- samples$alpha_low[,,]
alpha_high <- samples$alpha_high[,,]
alpha <- samples$alpha[,,]

plot(density(alpha_low[1,]), xlim=c(225,max(alpha_low)), lwd=2, col="purple4",
     main=expression(paste(alpha,"-low")), cex.main=1.2)
lines(density(alpha_low[2,]), col="indianred4", lwd=1.5)
legend("topleft",c("Control","Relational"),col=(c("purple4","indianred4")),lwd=2,cex=0.6)


plot(density(alpha_high[1,]), xlim=c(229,232), lwd=2, col="purple4",
     main=expression(paste(alpha,"-high")), cex.main=1.2)
lines(density(alpha_high[2,]), col="indianred4", lwd=1.5)


x <- seq(1,length(alpha_low[1,]),length.out=5000)
plot(alpha_low[1,x], pch=16, cex=0.5, type="l", ylab=expression(paste(alpha_low)), 
     xlab="Iteration", col="darkgoldenrod3", ylim=c(140,250))
x <- seq(1,length(alpha_low[2,]),length.out=5000)
lines(alpha_low[2,], pch=16, cex=0.5, type="l", col="indianred2")
x <- seq(1,length(alpha_high[2,]),length.out=5000)
lines(alpha_high[2,], pch=16, cex=0.5, type="l", col="red",lty=2)
x <- seq(1,length(alpha_high[1,]),length.out=5000)
lines(alpha_high[1,], pch=16, cex=0.5, type="l", col="green",lty=2)


predPost1 <- runif(length(alpha_low[1,]),alpha_low[1,],alpha_high[1,])
predPost2 <- runif(length(alpha_low[2,]),alpha_low[2,],alpha_high[2,])
plot(density(predPost1), xlim=c(225,231), lwd=2, col="purple4", ylim=c(0,1.2),
     main=expression(paste(alpha,"- Posterior")), cex.main=1.2)
lines(density(predPost2), cex=0.5, type="l", col="indianred2")
```

```{r}
par(mfrow=c(2,2))

tau_low <- samples$tau_low[,,]
tau_high <- samples$tau_high[,,]

tau <- samples$tau[,,]


plot(density(tau_low[1,]), xlim=c(min(tau_low),max(tau_low)), lwd=2, col="darkgoldenrod3", 
     main=expression(paste(tau,"-low")), cex.main=1.2)
for(i in 2:J){lines(density(tau_low[i,]), col=i, lwd=1.5)}
legend("topleft",c("Control","Relational"),col=(c("darkgoldenrod3",2)),lwd=2,cex=0.6)

plot(density(tau_high[1,]), xlim=c(min(tau_high),max(tau_high)), lwd=2, col="darkgoldenrod3", 
     main=expression(paste(tau,"-high")), cex.main=1.2)
for(i in 2:J){lines(density(tau_high[i,]), col=i, lwd=1.5)}

x <- seq(1,length(tau_low[1,]),length.out=5000)
plot(tau_low[1,x], pch=16, cex=0.5, type="l", ylab=expression(paste(tau_low/up)), 
     xlab="Iteration", col="darkgoldenrod3")#, ylim=c(370,500))
x <- seq(1,length(tau_low[2,]),length.out=5000)
lines(tau_low[2,], pch=16, cex=0.5, type="l", col="indianred2")
x <- seq(1,length(tau_high[2,]),length.out=5000)
lines(tau_high[2,], pch=16, cex=0.5, type="l", col="indianred2",lty=2)
x <- seq(1,length(tau_high[1,]),length.out=5000)
lines(tau_high[1,], pch=16, cex=0.5, type="l", col="darkgoldenrod3",lty=2)

predPost1 <- runif(length(tau_low[1,]),tau_low[1,],tau_high[1,])
predPost2 <- runif(length(tau_low[2,]),tau_low[2,],tau_high[2,])
plot(density(predPost1), lwd=2, col="darkgoldenrod3",
     main=expression(paste(tau,"- Posterior")), cex.main=1.2)
lines(density(predPost2), cex=0.5, type="l", col=2)
```



```{r}
par(mfrow=c(2,2))

mu.nu1 <- samples$mu.nu[1,,]
mu.nu2 <- samples$mu.nu[2,,]

sigma.nu1 <- samples$sigma.nu[1,,]
sigma.nu2 <- samples$sigma.nu[2,,]

nu1 <- samples$nu[1,,,]
nu2 <- samples$nu[2,,,]

plot(density(mu.nu1), xlim=c(-.7,0.7), lwd=2, col="darkgoldenrod3", 
     main=expression(paste(mu,"_",nu)), cex.main=1.2)
lines(density(mu.nu2), col=2, lwd=1.5)
legend("topleft",c("Control","Relational"),col=(c("darkgoldenrod3",2)),lwd=2,cex=0.6)

plot(density(sigma.nu1), xlim=c(0,0.7), lwd=2, col="darkgoldenrod3", 
     main=expression(paste(sigma,"_",nu)), cex.main=1.2)
lines(density(sigma.nu2), col=2, lwd=1.5)


x <- seq(1,length(nu1),length.out=5000)
plot(nu1[x], pch=16, cex=0.5, type="l", ylab=expression(paste(nu)), 
     xlab="Iteration", col="darkgoldenrod3", ylim=c(-0.01,0.01))
x <- seq(1,length(nu2),length.out=5000)
lines(nu2[x], pch=16, cex=0.5, type="l", col="indianred2")

plot(density(nu1), xlim=c(min(nu1),max(nu1)), lwd=2, col="darkgoldenrod1",
     main=expression(paste(nu)), cex.main=1.2)
lines(density(nu2), col="indianred2", lwd=1.5)


```