---
title: "Modeling 101-A: A Wiener per Task"
author: "Adriana F. Chávez De la Peña"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(R2jags)  #Load up packages
library(brms)
library(dplyr)

# Run from home (PV 2104)
load.module(name="wiener",
            path="/usr/lib/x86_64-linux-gnu/JAGS/lib/JAGS/modules-4/")

# Run from office
#load.module(name="wiener",
#            path="/usr/lib/JAGS/modules-4/")
```

```{r, eval=FALSE}
#library(RWiener)

#Y <- rwiener(1000,alpha=100,delta=1,tau=1,beta = 0.5)
#hist(Y$q, breaks=20)
```

# Load the data

```{r}
datos <- read.csv("../00_RawMaterial/datos.csv")
rt.0 <- which(datos$rt==0)
datos <- datos[-rt.0,]

I <- length(unique(datos$subID))
J <- length(unique(datos$cond))
N <- nrow(datos)

RT <- datos$rt/1000
C <- datos$resp

task <- rep(2,N)
task[datos$cond=="control"] <- 1

sub <- as.factor(datos$subID)
levels(sub) <- c(1:I)

Y<-RT
Y[C==0] <- -RT[C==0]

get.init <- function(a,b){b+((a-b)/2)}
```

# The model

\begin{align*}
Y = (Choice,RT)
\end{align*}

\begin{align*}
Y_{ijk} \sim \mbox{Wiener}(\alpha_j,\tau_j,\beta_j,\delta_j)
\end{align*}

with uninformative priors:

\begin{align*}
\alpha_j \sim \mbox{Uniform}(0,100)\\
\tau_j \sim \mbox{InverseGamma}(0.5,0.5)\\
\beta_j \sim \mbox{Uniform}(0,1)\\
\delta_j \sim \mbox{Normal}(0,20)\\
\end{align*}

where:

\begin{align*}
\alpha && \mbox{Threshold separation} && \alpha &> 0\\
\tau && \mbox{Non-decision time} && \tau &> 0\\
\beta && \mbox{Bias towards "Yes"} && 0 < &\beta < 1\\
\delta && \mbox{Drift rate} && \delta \sim &\mbox{Normal}(0,1)\\
\end{align*}

```{r original-code, eval=FALSE}
write('
model {

    # Alpha = Boundary distance
    mu.alpha ~ dunif(0.02,0.30)
    sigma.alpha ~ dunif(0.0001,0.15)
    prec.alpha <- pow(sigma.alpha,-2)
    
    beta <- 0.5
    
    # Theta = Mean ND-RT
    mu.theta ~ dunif(0.02,0.70)
    sigma.theta ~ dunif(0.0001,0.15)
    prec.theta <- pow(sigma.theta,-2)
    
    # Ji = Variance on ND-RT
    mu.chi ~ dunif(0.0001,0.15)
    sigma.chi ~ dunif(0.0001,0.10)
    prec.chi <- pow(sigma.chi,-2)
    
    # Eta = Variance on drift rate
    mu.eta ~ dunif(0.001,0.45)
    sigma.eta ~ dunif(0.0001,0.15)
    prec.eta <- pow(sigma.eta,-2)

    for(i in 1:J){
      # Nu = Mean drift rate
      mu.nu[i] ~ dunif(-.5,.6)
      sigma.nu[i] ~ dunif(0,0.6)
      prec.nu[i] <- pow(sigma.nu[i],-2)
    }

    for(p in 1:I){
    
      # Alpha = Boundary distance
      alpha[p] ~ dnorm(mu.alpha,prec.alpha)T(0.01,0.25)
      # Theta = Mean ND-RT
      theta[p] ~ dnorm(mu.theta,prec.theta)T(0.01,0.80)
      # Ji = Variance on ND-RT
      chi[p] ~ dnorm(mu.chi,prec.chi)T(0.00001,0.49)
      prec.tau[p] <- pow(chi[p],-2)
      # Eta = Variance on drift rate
      eta[p] ~ dnorm(mu.eta,prec.eta)T(0.00001,0.49)
      prec.delta[p] <- pow(eta[p],-2)
  
        # For each participant, theres a condition-level distribution
        for(i in 1:J){
            # Nu = Mean drift rate
            nu[p,i] ~ dnorm(mu.nu[i],prec.nu[i])T(-.7,.7)
        }
      }

    for (i in 1:N) {
      # Trial-by-trial variability in ND-RT and drift rates
      tau[i] ~ dnorm(theta[sub[i]],prec.tau[sub[i]])T(0,)
      delta[i] ~ dnorm(nu[sub[i],task[i]],prec.delta[sub[i]])T(0,)
    
      Y[i] ~ dwiener(alpha[sub[i]],tau[i],beta,delta[i])
    }
  

}',  'wiener_w8_1.txt')
```

```{r my-own-priors, eval=TRUE}
write('
model {

    # Alpha = Boundary distance
    mu.alpha ~ dunif(0.01,50)
    sigma.alpha ~ dunif(0.0001,50)
    prec.alpha <- pow(sigma.alpha,-2)
    
    beta <- 0.5
    
    # Theta = Mean ND-RT
    mu.theta ~ dunif(0.02,50)
    sigma.theta ~ dunif(0.0001,15)
    prec.theta <- pow(sigma.theta,-2)
    
    # Ji = Variance on ND-RT
    mu.chi ~ dunif(0.0001,50)
    sigma.chi ~ dunif(0.0001,20)
    prec.chi <- pow(sigma.chi,-2)
    
    # Eta = Variance on drift rate
    mu.eta ~ dunif(0.001,45)
    sigma.eta ~ dunif(0.0001,55)
    prec.eta <- pow(sigma.eta,-2)

    for(i in 1:J){
      # Nu = Mean drift rate
      mu.nu[i] ~ dunif(-10,10)
      sigma.nu[i] ~ dunif(0.001,60)
      prec.nu[i] <- pow(sigma.nu[i],-2)
    }

    for(p in 1:I){
    
      # Alpha = Boundary distance
      alpha[p] ~ dnorm(mu.alpha,prec.alpha)T(0.0001,)
      # Theta = Mean ND-RT
      theta[p] ~ dnorm(mu.theta,prec.theta)T(0.01,0.80)
      # Ji = Variance on ND-RT
      chi[p] ~ dnorm(mu.chi,prec.chi)T(0.00001,0.49)
      prec.tau[p] <- pow(chi[p],-2)
      # Eta = Variance on drift rate
      eta[p] ~ dnorm(mu.eta,prec.eta)T(0.00001,0.49)
      prec.delta[p] <- pow(eta[p],-2)
  
        # For each participant, theres a condition-level distribution
        for(i in 1:J){
            # Nu = Mean drift rate
            nu[p,i] ~ dnorm(mu.nu[i],prec.nu[i])
        }
      }

    for (i in 1:N) {
      # Trial-by-trial variability in ND-RT and drift rates
      tau[i] ~ dnorm(theta[sub[i]],prec.tau[sub[i]])T(0,)
      delta[i] ~ dnorm(nu[sub[i],task[i]],prec.delta[sub[i]])T(0,)
    
      Y[i] ~ dwiener(alpha[sub[i]],tau[i],beta,delta[i])
    }
  

}',  'wiener_w8_1.txt')
```

```{r}
y = Y

dat <- list(Y=y,N=N,I=I,J=J,sub=sub,task=task)

inits <- list(mu.alpha=0.16,sigma.alpha=0.075,
              mu.eta=0.225,sigma.eta=0.075,
              mu.chi=0.075,sigma.chi=0.05,
              mu.theta=0.36,sigma.theta=0.075,
              mu.nu=rep(0.05,J),sigma.nu=rep(0.3,J))

model <- jags.model("./wiener_w8_1.txt",data=dat,
                    inits=inits,n.chains=1,n.adapt=0)

samples <- jags.samples(model,
                        c("mu.alpha","sigma.alpha","mu.eta","sigma.eta","mu.chi",
                          "sigma.chi","mu.theta","sigma.theta"),n.iter=1000,thin=1)
```



```{r}
alpha <- samples$alpha[,,]
beta <- samples$beta[,,]
delta <- samples$delta[,,]
tau <- samples$tau[,,]
```

```{r}
par(mfrow=c(2,2))

plot(density(alpha[1,]), xlim=c(min(alpha),max(alpha)), lwd=2, col="purple4", main=expression(paste(alpha)),
     cex.main=3,ylim=c(0,3.5))
for(i in 2:I){
  lines(density(alpha[i,]), col=i, lwd=1.5)}

plot(density(beta[1,]), xlim=c(min(beta),max(beta)), lwd=2, col="purple4", main=expression(paste(beta)),
     cex.main=3, ylim=c(0,7))
for(i in 2:I){
  lines(density(beta[i,]), col=i, lwd=1.5)}

plot(density(delta[,2]), xlim=c(min(delta),max(delta)), lwd=2, col="purple4", main=expression(paste(delta)),
     cex.main=3, ylim=c(0,2))
for(i in 2:I){
  lines(density(delta[i,]), col=i, lwd=1.5)}

plot(density(tau[1,]), xlim=c(min(tau),max(tau)), lwd=2, col="purple4", main=expression(paste(tau)),
     cex.main=3,ylim=c(0,15))
for(i in 2:I){
  lines(density(tau[i,]), col=i, lwd=1.5)}
```