---
title: "Modeling 101-A: A Wiener per Task"
author: "Adriana F. Chávez De la Peña"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(R2jags)  #Load up packages
library(brms)
library(dplyr)

# Run from home (PV 2104)
load.module(name="wiener",
            path="/usr/lib/x86_64-linux-gnu/JAGS/lib/JAGS/modules-4/")

# Run from office
#load.module(name="wiener",
#            path="/usr/lib/JAGS/modules-4/")
```

```{r, eval=FALSE}
#library(RWiener)

#Y <- rwiener(1000,alpha=100,delta=1,tau=1,beta = 0.5)
#hist(Y$q, breaks=20)
```

# Load the data

```{r}
datos <- read.csv("../00_RawMaterial/datos.csv")
rt.0 <- which(datos$rt<50)
datos <- datos[-rt.0,]

I <- length(unique(datos$subID))
J <- length(unique(datos$cond))
N <- nrow(datos)

RT <- datos$rt
C <- datos$resp

task <- rep(2,N)
task[datos$cond=="control"] <- 1

sub <- as.factor(datos$subID)
levels(sub) <- c(1:I)

Y<-RT
Y[C==0] <- -RT[C==0]
```

# The model

\begin{align*}
Y = (Choice,RT)
\end{align*}

\begin{align*}
Y_{ijk} \sim \mbox{Wiener}(\alpha_j,\tau_j,\beta_j,\delta_j)
\end{align*}

with uninformative priors:

\begin{align*}
\alpha_j \sim \mbox{Uniform}(0,100)\\
\tau_j \sim \mbox{InverseGamma}(0.5,0.5)\\
\beta_j \sim \mbox{Uniform}(0,1)\\
\delta_j \sim \mbox{Normal}(0,20)\\
\end{align*}

where:

\begin{align*}
\alpha && \mbox{Threshold separation} && \alpha &> 0\\
\tau && \mbox{Non-decision time} && \tau &> 0\\
\beta && \mbox{Bias towards "Yes"} && 0 < &\beta < 1\\
\delta && \mbox{Drift rate} && \delta \sim &\mbox{Normal}(0,1)\\
\end{align*}

```{r}
write('
model {
  #Likelihood
  for (i in 1:N) {
    Y[i] ~ dwiener(alpha,tau[task[i]],beta[task[i]],delta[i])
    delta[i] ~ dnorm(mu[sub[i],task[i]],lambda[sub[i],task[i]])
  }
  for(a in 1:I){
    for(c in 1:J){
      mu[a,c] ~ dnorm(nu[c],eta)
      lambda[a,c] ~ dgamma(lambda_s,lambda_r)
    }
  }
  
  #Priors
  for (j in 1:J) {
  beta[j] ~ dunif(beta_low[j],beta_high[j])
  beta_high[j] ~ dunif(0,1)
  beta_low[j] ~ dunif(0.01,beta_high[j])
  tau[j] ~ dunif(tau_low[j],tau_high[j])
  tau_high[j] ~ dunif(0.01,1000)
  tau_low[j] ~ dunif(0,tau_high[j])
  nu[j] ~ dnorm(0,10^-5)
  }
  alpha ~ dunif(alpha_low,alpha_high)
  alpha_high ~ dunif(0,1000)
  alpha_low ~ dunif(0.01,alpha_high)
  lambda_s ~ dunif(0,100)
  lambda_r ~ dunif(0,100)
  eta ~ dgamma(2,2)
}',  'wienerW5b.txt')
```

```{r}
dat <- list(Y=Y,N=N,I=I,J=J,task=task,sub=sub)
inits <- list(alpha_high=10,alpha_low=5,
              lambda_s = 2, lambda_r =2,
              tau_high=rep(200,J),tau_low=rep(10,J),
              beta_high=rep(0.8,J),beta_low=rep(0.2,J),
              nu = rep(0,J), eta=30
              )
model <- jags.model("./wienerW5b.txt",data=dat,n.chains=1,n.adapt=0,inits=inits)
samples <- jags.samples(model,c("alpha","beta","tau", "delta",
                                "alpha_low","alpha_high"),n.iter=1000,thin=1)
```

```{r}
alpha <- samples$alpha[,,]
beta <- samples$beta[,,]
delta <- samples$delta[,,]
tau <- samples$tau[,,]

```

```{r}
par(mfrow=c(2,2))

alpha_low <- samples$alpha_low[,,]
alpha_high <- samples$alpha_high[,,]


alpha <- samples$alpha[,,]


plot(density(alpha_low), xlim=c(min(alpha_low),max(alpha_low)), lwd=2, col="purple4",
     main=expression(paste(alpha,"-low")), cex.main=1.2)

plot(density(alpha_high), xlim=c(min(alpha_high),max(alpha_low)), lwd=2, col="purple4",
     main=expression(paste(alpha,"-high")), cex.main=1.2)

predPost <- runif(length(alpha_low),mean(alpha_low),mean(alpha_high))
plot(density(predPost), xlim=c(min(predPost),max(predPost)), lwd=2, col="purple4",
     main=expression(paste(alpha,"- Inferred Parent")), cex.main=1.2)

plot(density(alpha), xlim=c(min(alpha),max(alpha)), lwd=2, col="cyan4",
     main=expression(paste(alpha,"- Posterior samples")), cex.main=1.2)
```

```{r}
par(mfrow=c(2,2))

plot(density(alpha[1,]), xlim=c(min(alpha),max(alpha)), lwd=2, col="purple4", main=expression(paste(alpha)),
     cex.main=3,ylim=c(0,3.5))
for(i in 2:I){
  lines(density(alpha[i,]), col=i, lwd=1.5)}

plot(density(beta[1,]), xlim=c(min(beta),max(beta)), lwd=2, col="purple4", main=expression(paste(beta)),
     cex.main=3, ylim=c(0,7))
for(i in 2:I){
  lines(density(beta[i,]), col=i, lwd=1.5)}

plot(density(delta[,2]), xlim=c(min(delta),max(delta)), lwd=2, col="purple4", main=expression(paste(delta)),
     cex.main=3, ylim=c(0,2))
for(i in 2:I){
  lines(density(delta[i,]), col=i, lwd=1.5)}

plot(density(tau[1,]), xlim=c(min(tau),max(tau)), lwd=2, col="purple4", main=expression(paste(tau)),
     cex.main=3,ylim=c(0,15))
for(i in 2:I){
  lines(density(tau[i,]), col=i, lwd=1.5)}
```