 ---
title: "Hierarchical Model 1"
author: "Adriana F. Chávez De la Peña"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(R2jags)  #Load up packages
library(brms)
library(dplyr)

# Run from home (PV 2104)
load.module(name="wiener",
            path="/usr/lib/x86_64-linux-gnu/JAGS/lib/JAGS/modules-4/")
```


# Load the data

```{r}
datos <- read.csv("../../../../RawData/datos.csv")
datos <- datos[-which(datos$rt<50),]
datos <- datos[-which(datos$subID=="735148")]

N <- nrow(datos)
RT <- datos$rt
C <- datos$resp
#C <- datos$acc

J <- length(unique(datos$cond))
task <- rep(2,N)
task[datos$cond=="control"] <- 1

I <- length(unique(datos$subID))
subj <- as.factor(datos$subID)
levels(subj) <- c(1:I)

Y<-RT
Y[C==0] <- -RT[C==0]
```

# The model

We model the Bivariate data $Y_{ijk}$ that contains the Choices and RTs observed for every participant $i$, on condition $j$ and trial $k$, as:

\begin{align*}
Y_{ijk} \sim \mbox{Wiener}(\alpha_{j},\tau_{i},\beta_{j},\delta_{ijk})\\
\delta_{ijk} \sim \mbox{Normal}(\nu_{ij},\sigma_\delta)\\
\end{align*}

with hyperparameters:

\begin{align*}
\alpha_{j} \sim \mbox{Normal}(\mu_\alpha,\sigma_\alpha)\\
\beta_{j} \sim \mbox{Normal}(\mu_\beta,\sigma_\beta)\\
\tau_{i} \sim \mbox{Normal}(\mu_\tau,\sigma_\tau)\\
\nu_{ij} \sim \mbox{Normal}(\mu_\nu,\sigma_\nu)\\
\end{align*}

and **widely uninformative priors.**


```{r}
write('
model {
  
  ###### Trial-by-trial variation
  for (i in 1:N) {
    Y[i] ~ dwiener(alpha[task[i]],tau[subj[i]],beta[task[i]],delta[i])
    delta[i] ~ dnorm(nu[subj[i],task[i]],precDelta)
  }
  
  ###### Task-by-Participant mean drift rate
  for(i in 1:I){
    for(j in 1:J){
        nu[i,j] ~ dnorm(muNu,precNu)
    }
  }
  
  ###### Task-by-Participant mean drift rate
  for(i in 1:I){
      tau[i] ~ dnorm(muTau,precTau)
  }
  
  ###### Task-by-Participant mean drift rate
  for(j in 1:J){
      alpha[j] ~ dnorm(muAlpha,precAlpha)
      beta[j] ~ dnorm(muBeta,precBeta)
  }
  
  ################ PRIORS
  muBeta ~ dunif(0,1)
  muAlpha ~ dunif(0,500)
  muTau ~ dunif(0,2000)
  muNu ~ dnorm(0,300)
  
  sigmaBeta ~ dunif(0.0001,1000)
  sigmaAlpha ~ dunif(0.0001,1000)
  sigmaTau ~ dunif(0.0001,1000)
  sigmaNu ~ dnorm(0.0001,1000)
  sigmaDelta ~ dnorm(0.0001,1000)
  
  precBeta <- pow(sigmaBeta,-2) 
  precAlpha <- pow(sigmaAlpha,-2) 
  precTau <- pow(sigmaTau,-2) 
  precNu <- pow(sigmaNu,-2) 
  precDelta <- pow(sigmaDelta,-2) 
  
  
}',  'hierarchical_1.txt')
```

```{r}
y = Y*1000

dat <- list(Y = y,
            N = N,
            I = I,
            J = J,
            subj = subj,
            task = task)

inits <- list(alpha_high=rep(30,J),alpha_low=rep(10,J),
              tau_high=rep(200,J),tau_low=rep(10,J),
              mu.nu = rep(50,J), sigma.nu = rep(1,J), eta=10
              )
model <- jags.model("./hierarchical_1.txt",data=dat,n.chains=1,n.adapt=0)#,inits=inits)
samples <- jags.samples(model,
                        c("alpha","beta","tau","delta","nu","sigmaDelta",
                          "muAlpha","muBeta","muTau","muNu",
                          "sigmaAlpha","sigmaBeta","sigmaTau","sigmaNu"), n.iter=10000,thin=1)

save(samples,file="./samples.RData")
```

```{r}
alpha <- samples$alpha[,,]
beta <- samples$beta[,,]
delta <- samples$delta[,,]
tau <- samples$tau[,,]
```

