---
title: "Modeling 101-A: A Wiener per Task"
author: "Adriana F. Chávez De la Peña"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(R2jags)  #Load up packages
library(brms)

# Run from home (PV 2104)
load.module(name="wiener",
            path="/usr/lib/x86_64-linux-gnu/JAGS/lib/JAGS/modules-4/")

# Run from office
#load.module(name="wiener",
#            path="/usr/lib/JAGS/modules-4/")
```

```{r, eval=FALSE}
#library(RWiener)

#Y <- rwiener(1000,alpha=100,delta=1,tau=1,beta = 0.5)
#hist(Y$q, breaks=20)
```

# Load the data

```{r}
datos <- read.csv("../00_RawMaterial/datos.csv")
rt.0 <- which(datos$rt==0)
datos <- datos[-rt.0,]

I <- length(unique(datos$subID))
J <- length(unique(datos$cond))
N <- nrow(datos)

RT <- datos$rt/1000
C <- datos$resp

task <- rep(2,N)
task[datos$cond=="control"] <- 1

sub <- as.numeric(datos$subID)

Y<-RT
Y[C==0] <- -RT[C==0]
```

# The model

\begin{align*}
Y = (Choice,RT)
\end{align*}

\begin{align*}
Y_{ijk} \sim \mbox{Wiener}(\alpha_j,\tau_j,\beta_j,\delta_j)
\end{align*}

with uninformative priors:

\begin{align*}
\alpha_j \sim \mbox{Uniform}(0,100)\\
\tau_j \sim \mbox{InverseGamma}(0.5,0.5)\\
\beta_j \sim \mbox{Uniform}(0,1)\\
\delta_j \sim \mbox{Normal}(0,20)\\
\end{align*}

where:

\begin{align*}
\alpha && \mbox{Threshold separation} && \alpha &> 0\\
\tau && \mbox{Non-decision time} && \tau &> 0\\
\beta && \mbox{Bias towards "Yes"} && 0 < &\beta < 1\\
\delta && \mbox{Drift rate} && \delta \sim &\mbox{Normal}(0,1)\\
\end{align*}

```{r}
write('
model {
  for (i in 1:N) {
    Y[i] ~ dwiener(alpha[task[i]],tau[task[i]],beta[task[i]],delta[task[i]])
  }
  for (j in 1:J) {
  alpha[j] ~ dunif(-5,5)
  tau[j] ~ dunif(0,1)
  beta[j] ~ dunif(0,1)
  delta[j] ~ dunif(-5,5)
  }
}',  'wiener01a.txt')
```

```{r}
dat <- list(Y=Y,N=N,J=J,task=task)
inits <- list(alpha=rep(1,J),tau=rep(0.001,J),
              beta=rep(0.5,J),delta=rep(0,J))
model <- jags.model("./wiener01a.txt",data=dat,inits=inits,n.chains=1,n.adapt=0)
samples <- jags.samples(model,c("alpha","tau","beta","delta"),n.iter=1000,thin=1)
```

```{r}
alpha <- samples$alpha[,,]
alpha <- cbind(alpha[1,],alpha[2,])

beta <- samples$beta[,,]
beta <- cbind(beta[1,],beta[2,])

delta <- samples$delta[,,]
delta <- cbind(delta[1,],delta[2,])

tau <- samples$tau[,,]
tau <- cbind(tau[1,],tau[2,])
```

```{r}
par(mfrow=c(2,2))
plot(density(alpha[,1]), xlim=c(min(alpha),max(alpha)), lwd=2, col="purple4", main=expression(paste(alpha)),cex.main=3)
for(j in 2:J){
  lines(density(alpha[,j]), col=j, lwd=2)}
legend("topright",c("Relational","Control"), col=c("red","purple4"), lwd=2, cex=0.7)

plot(density(beta[,1]), xlim=c(min(beta),max(beta)), lwd=2, col="purple4", main=expression(paste(beta)),cex.main=3)
for(j in 2:J){
  lines(density(beta[,j]), col=j, lwd=2)}

plot(density(delta[,2]), xlim=c(min(delta),max(delta)), lwd=2, col="purple4", main=expression(paste(delta)),cex.main=3)
for(j in 2:J){
  lines(density(delta[,1]), col=j, lwd=2)}

plot(density(tau[,1]), xlim=c(min(tau),max(tau)), lwd=2, col="purple4", main=expression(paste(tau)),cex.main=3)
for(j in 2:J){
  lines(density(tau[,j]), col=j, lwd=2)}
```